---
title: "Exploring the BRFSS data"
output: 
  html_document: 
    fig_height: 4
    highlight: pygments
    theme: spacelab
---

## Setup

### Load packages

```{r load-packages, message = FALSE}
library(ggplot2)
library(dplyr)
library(knitr)
```

### Load data

```{r load-data}
load("brfss2013.RData")
df = brfss2013
```

* * *

## Part 1: Data

The Behavioral Risk Factor Surveillance System (BRFSS) is "a collaborative project between all of the states in the United States (US) and participating US territories and the Centers for Disease Control and Prevention (CDC)."

According to the Overview text "The BRFSS objective is to collect uniform, state-specific data on preventive health practices and risk behaviors that are linked to chronic diseases, injuries, and preventable infectious diseases that affect the adult population."

The data is collected using telephone and cellular telephone-based surveys. In conducting the BRFSS landline telephone survey, interviewers collect data from a randomly selected adult in a household. In conducting the cellular telephone version of the BRFSS questionnaire, interviewers collect data from an adult who participates by using a cellular telephone and resides in a private residence or college housing.

The data are transmitted to the CDC for editing, processing, weighting, and analysis. An edited and weighted data file is provided to each participating health department for each year of data collection, and summary reports of state-specific data are prepared by the CDC. 

* * *

## Part 2: Research questions

**Research quesion 1:** What is the behavior of fruits and vegetables by status of health? 

In this question we will try to understand the daily behavior of natural juices, vegetables and beans according the declared health status of intervierws. Our hipotheses is that the people with a daily consumption of fruits, juices and vegetables has excellent and good health status. 

**Research quesion 2:** male or female consumes more fruits and vegetables? 

**Research quesion 3:**  the people who consumes more fruits has chronic problem?


* * *

## Part 3: Exploratory data analysis

**Research quesion 1:**

### Separate variables
```{r echo=FALSE, results=FALSE}
df %>%
  select(genhlth, fruitju1, fvgreen, vegetab1)
```

### Descriptive analysis of variables

Below we will to analysis 4 variables: genhlth, fruitjui1, fvgreen, vegetab1. 
For each variable we check the factors and the proportion for each one. After that, we will select some factors related to periodic to analyse and to the end we make analysis comparing the health status with the food that we analyzed. 

### Health Status description - genhlth variable
```{r}
Percentage = prop.table(table(df$genhlth))
Frequencies = summary(df$genhlth)
Frequencies = Frequencies[1:5]
genhlth_df = data.frame(Frequencies, Percentage)
genhlth_df = genhlth_df[,-2]
```

```{r}
kable(genhlth_df, caption = "Health Status Table")
```

Note that the most part of interviewrs (80%) declaring Excellent and Good Health Status.

### Frequencies of Healthy foods consumption

To this analysis we focusing our sample to individuals that consumes this kind of food per day or not consuming. The survey calculated too the consume with week and month period but we are interesting in the daily consumption. 

```{r echo=FALSE, results= FALSE}
### Juice
prop.fruits = df %>% 
      filter(fruitju1 <= 299 & fruitju1 >=201)

prop.fruits = as.data.frame(table(prop.fruits$fruitju1))
`row.names<-`(prop.fruits, prop.fruits$Var1)

### Veg
prop.veg = df %>% 
      filter(vegetab1 <= 299 & vegetab1 >=201)

prop.veg = as.data.frame(table(prop.veg$vegetab1))
`row.names<-`(prop.veg, prop.veg$Var1)

### Beens
prop.beens = df %>% 
      filter(fvgreen <= 299 & fvgreen >=201)

prop.beens = as.data.frame(table(prop.beens$fvgreen))
`row.names<-`(prop.beens, prop.beens$Var1)

### Proportion of 1 to 3 times per day of consumption
sumfruit = sum(prop.fruits[c(1:3),2])/sum(prop.fruits[,2])
sumveg = sum(prop.veg[c(1:3),2])/sum(prop.veg[,2])
sumbeens = sum(prop.beens [c(1:3),2])/sum(prop.beens [,2])
```

```{r echo=FALSE, fig.show='hold',fig.align='center', fig.width=15, fig.height=5}
par(mfrow = c(1, 3))
barplot(prop.fruits$Freq, names.arg=prop.fruits$Var1, cex.names=0.8, ylim = c(0,90000), col = "red", main = "Frequencies of Fruits Consumption per day")
barplot(prop.veg$Freq, names.arg=prop.veg$Var1, cex.names=0.8, ylim = c(0,130000), col = "Orange", main = "Frequencies of Vegetables Consumption per day")
barplot(prop.beens$Freq, names.arg=prop.beens$Var1, cex.names=0.8, ylim = c(0,70000), col = "blue", main = "Frequencies of Beans Consumption per day")
```

Note that the most frequencies of consumption per day ocurr at 101 and 105 at most. Make analysis more precisely we identified that the most ocurrencies is between 1 and 3 times per day. For the Fruits the frequencies of 1 to 3 times per day is 97%, vegetables and beans 98%. In this case, we considering to our sample just the interviewrs that respond that the consumption of fruits, beens and vegetables is between 1 to 3. 



**Research quesion 2:**



**Research quesion 3:**

```{r}

```

